Layered Grammar for Alluvial Plots

### 2020-01-17 paper.rmd
edit 'easy' footnote following edits to surrounding text

[^easy]: Other ggplot2 extensions are not so flexible; in particular, the dependency package easyalluvial [@Koneswarakantha2019] was built on top of ggalluvial to exchange much of this flexibility for more expedient data exploration.

>>>>

[^easy]: Indeed, the dependency package easyalluvial [@Koneswarakantha2019] was built on top of ggalluvial to exchange much of this flexibility for more expedient data exploration.
